Universal Anonymous Signatures

### 2022-07-18 prism-backend/research/gsac/app-building-blocks.tex
Applying comments by Markulf.

\paragraph{Augmenting with NIZKs.} %
\todo{This is quite informal. Perhaps expand...} 
In the previous \SBCM scheme, it is straightforward to require that the party
running \SBCMCom proves some arbitrary claim over the messages to be signed
(both those in committed or plaintext form). This can be done by having this
party add a NIZK over the corresponding NP statement, which has later to be
verified by the party running \SBCMSign. We will be using this extension, and
use $\SBCM^{\NIZKRel}$ to denote such an \SBCM with proofs for claims in
\NIZKRel.

@@

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

>>>>

\paragraph{Augmenting with NIZKs.} %
\todo{This is quite informal. Perhaps expand...} 
In the previous \SBCM scheme, it is straightforward to require that the party
running \SBCMCom proves some arbitrary claim over the messages to be signed
(both those in committed or plaintext form), as well as over possibly extra
auxiliary data. This can be done by having this party add a NIZK over the
corresponding NP statement, which has later to be verified by the party running
\SBCMSign.
%
We use this extension in our \CUASGen construction, and thus extend the previous
syntax for interactive signing  as follows, to account for an extra NIZK
relation \NIZKRel proving that a pair of statement $x$ and witness $w$ belong
\NIZKRel.

\begin{description}
\item[$\SBCMsig/\bot \gets \langle \SBCMCom^{\NIZKRel}(\SBCMvk,\overline{\smsg},
  \smsg,(x,w)),\SBCMSign^{\NIZKRel}(\SBCMsk,\smsg,x) \rangle$.] As before, but
  the party running \SBCMCom, who owns witness $w$ for $x$ in \NIZKRel, proves
  in zero-knowledge to the party running \SBCMSign that $(x,w) \in \NIZKRel$.
\end{description}

@@

Note that, if needed, it is straightforward to augment the proof \NIZKproof
produced by the user in the first step with an extended proof that also proves
that $(x,w) \in \NIZKRel$, for some other relation \NIZKRel, thus implementing
the augmented interface $\langle\SBCMCom^\NIZKRel,\SBCMSign^\NIZKRel\rangle$ as
described earlier.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas-paper"
%%% End:
